\begin{alltt}
# Thermohydraulique 2D couplee a conduction 2D #
# PARALLEL OK 8 #
dimension 2
Scheme_euler_explicit sch
Read sch
\{
    tinit 0.
    tmax 300.
    dt_min 0.001
    dt_max 10.
    dt_impr 0.001
    dt_sauv 400.
    seuil_statio 1.e-20
    {\bf{diffusion_implicite}}
\}
Pb_conduction pb1
Pb_Thermohydraulique pb2
Domaine dom_solide
Domaine dom_fluide
# BEGIN MESH #
Mailler dom_solide
\{
    Pave Cavite1
    \{
        Origine 0. 0.
        {\bf{Nombre_de_Noeuds 13 41}}
        Longueurs 0.3 1
    \}
    \{
        Bord Gauche1 X = 0.    0.  <= Y <= 1
        Bord Haut1   Y = 1     0.  <= X <= 0.3
        Bord Bas1    Y = 0.    0.  <= X <= 0.3
        Raccord local homogene Droit1  X = 0.3  0.3 <= Y <= 1
    \} ,
    Pave Cavite2
    \{
        Origine 0.3 0.
        {\bf{Nombre_de_Noeuds 29 13}}
        Longueurs 0.7 0.3
    \}
    \{
        Raccord local homogene Haut2   Y = 0.3  0.3 <= X <= 1
        Bord Bas2    Y = 0.   0.3 <= X <= 1
        Bord Droit2  X = 1    0.  <= Y <= 0.3
    \}
\}
Mailler dom_fluide
\{
    Pave Cavite3
    \{
        Origine 0.3 0.3
        {\bf{Nombre_de_Noeuds 29 29}}
        Longueurs 0.7 0.7
    \}
    \{
        Raccord local homogene Droit1 X = 0.3  0.3 <= Y <= 1
        Bord Entree    Y = 1  0.3 <= X <= 0.7
        Bord Haut3     Y = 1  0.7 <= X <= 1
        Raccord local homogene Haut2  Y = 0.3  0.3 <= X <= 1
        Bord Sortie    X = 1  0.3 <= Y <= 0.7
        Bord Droit2    X = 1  0.7 <= Y <= 1
    \}
\}
{\bf{trianguler_H dom_fluide}}
{\bf{trianguler_H dom_solide}}
{\bf{Transformer dom_fluide  X*(1-0.5*Y*Y)  Y*(1+0.1*X*Y)}}
{\bf{Transformer dom_solide  X*(1-0.5*Y*Y)  Y*(1+0.1*X*Y)}}
Postraiter_domaine \{ format lata fichier dom.lata domaines \{ dom_solide dom_fluide \} \}
# END MESH #
# BEGIN PARTITION
Partition dom_solide
\{
    Partition_tool tranche \{ tranches 3 1 \}
    Larg_joint 1
    zones_name DOM1
\}
Partition dom_fluide
\{
    Partition_tool tranche \{ tranches 3 1 \}
    Larg_joint 1
    zones_name DOM2
\}
End
END PARTITION #
# BEGIN SCATTER
Scatter DOM1.Zones dom_solide
Scatter DOM2.Zones dom_fluide
END SCATTER #
{\bf{VEFPreP1B dis}}
Fluide_Incompressible fluide
Read fluide
\{
    mu Champ_Uniforme 1 0.002
    rho Champ_Uniforme 1 2
    lambda Champ_Uniforme 1 1.0 
    Cp Champ_Uniforme 1 500
    beta_th Champ_Uniforme 1 0.0001
\}
Solide sol
Read sol
\{
    rho Uniform_Field 1 1000.
    lambda Champ_Uniforme 1 250.
    Cp Champ_Uniforme 1 100
\}
Uniform_field gravite
Read gravite 2 0 -9.81
Associate sol gravite
Associate fluide gravite
Associate pb1 dom_solide
Associate pb1 sol
Associate pb2 dom_fluide
Associate pb2 fluide
Probleme_Couple pbc
Associate pbc pb1
Associate pbc pb2
Associate pbc sch
Discretize pbc dis
Read pb1
\{
    Conduction
    \{
        diffusion \{ \}
        initial_conditions \{ temperature Champ_Uniforme 1 30. \}
        boundary_conditions
        \{
            Gauche1 paroi_temperature_imposee   Champ_Front_Uniforme 1 40.
            Haut1   paroi_temperature_imposee   Champ_Front_Uniforme 1 20.
            Bas1    paroi_temperature_imposee   Champ_Front_Uniforme 1 40.
            Droit1  paroi_contact pb2  Droit1   Haut2   paroi_contact pb2  Haut2
            Bas2    paroi_temperature_imposee   Champ_Front_Uniforme 1 40.
            Droit2  paroi_temperature_imposee   Champ_Front_Uniforme 1 20.
        \}
    \}
    Post_processing
    \{
        Probes
        \{
            sonde_tsol temperature periode 1. points 2     0.15 0.55     0.55 0.15 
        \}
        Definition_champs 
        \{
            temperature_elem_dom_solide Interpolation
            \{
                localisation elem
                source refChamp \{ Pb_champ pb1 temperature \}
            \}
            temperature_som_dom_solide Interpolation 
            \{
                localisation som
                source refChamp \{ Pb_champ pb1 temperature \}
            \}
        \}
        {\bf{Format lata}}
        fields dt_post 20.+2.*t
        \{
            temperature_elem_dom_solide
            temperature_som_dom_solide
            temperature elem
        \}
    \}
    sauvegarde formatte solide.rep
\}
Read pb2
\{
    Navier_Stokes_standard
    \{
        solveur_pression GCP \{ precond ssor \{ omega 1.500000 \} seuil 1.000000e-14 impr \}
        convection \{ amont \}
        diffusion \{ \}
        sources \{ boussinesq_temperature \{ T0 30. \} \}
        initial_conditions \{ vitesse Champ_Uniforme 2 0. 0. \}
        boundary_conditions \{
            Entree frontiere_ouverte_vitesse_imposee    Champ_front_Uniforme 2 0. -0.01
            Sortie frontiere_ouverte_pression_imposee   Champ_front_Uniforme 1 0.
            Droit1 paroi_fixe
            Haut3  paroi_fixe
            Haut2  paroi_fixe
            Droit2 paroi_fixe
        \}
    \}
    Convection_Diffusion_Temperature
    \{
        diffusion \{ \}
        convection \{ amont \}
        boundary_conditions 
        \{
            Entree frontiere_ouverte_temperature_imposee    Champ_front_Uniforme 1 20.
            Sortie frontiere_ouverte_temperature_imposee    Champ_front_Uniforme 1 20.
            Droit1 paroi_contact pb1  Droit1
            Haut3  paroi_temperature_imposee    Champ_front_Uniforme 1 20.
            Haut2  paroi_contact pb1  Haut2
            Droit2 paroi_temperature_imposee    Champ_front_Uniforme 1 20.
        \}
        initial_conditions \{ Temperature Champ_Uniforme 1 30. \}
    \}
    Post_processing
    \{
        Probes
        \{
            sonde_pression  pression periode 1.     points 1    0.55 0.55
            sonde_vitesse   vitesse periode 1.      points 1    0.55 0.55
            sonde_tflu      temperature periode 1.  points 1    0.55 0.55
            sonde_seg       temperature periode 5.  segment 10 0. 0.75 1. 0.75
            sonde_temp_interp_elem temperature_elem_dom_fluide periode 1. points 1   0.55 0.55
            sonde_temp_interp_som  temperature_som_dom_fluide  periode 1. points 1   0.55 0.55
            sonde_seg_temp_interp_elem temperature_elem_dom_fluide periode 5. 
                                                                    segment 10 0. 0.75 1. 0.75
        \}
        Definition_champs 
        \{
            temperature_elem_dom_fluide Interpolation
            \{
                localisation elem
                source refChamp \{ Pb_champ pb2 temperature \}
            \}
            temperature_som_dom_fluide Interpolation 
            \{
                localisation som
                source refChamp \{ Pb_champ pb2 temperature \}
            \}
        \}
        {\bf{Format lata}}
        fields dt_post 20.+2.*t
        \{
            pression elem
            pression som
            vitesse elem
            vitesse som
            temperature_elem_dom_fluide
            temperature_som_dom_fluide
        \}
    \}
    sauvegarde formatte fluide.rep
\}
Imprimer_flux dom_fluide \{ Entree Haut2 \}
Imprimer_flux dom_solide \{ Bas1 Haut2 \}
Solve pbc
End
\end{alltt}
