\begin{alltt}
# Hydraulique 2D turbulent K-Eps #
# PARALLEL OK 8 #
dimension 2
{\bf{Pb_Hydraulique_concentration_Turbulent pb}}
Domaine dom
# BEGIN MESH #
Mailler dom
\{
    Pave Entree
    \{
        Origine 0. 1.
        Nombre_de_Noeuds 8 6 
        Longueurs 7. 1.
    \}
    \{
        Bord Entree X = 0. 1. <= Y <= 2.
        Bord Haut1  Y = 2. 0. <= X <= 7.
        Bord Bas1   Y = 1. 0. <= X <= 7.
    \} ,
    Pave Haut
    \{
        Origine 7. 1.
        Nombre_de_Noeuds 11 6 
        Longueurs 10. 1.
    \}
    \{
        Bord Haut2  Y = 2.  7. <= X <= 17.
    \} ,
    Pave SHaute
    \{
        Origine 17. 1.
        Nombre_de_Noeuds 14 6 
        Longueurs 13. 1.
    \}
    \{
        Bord SortieHaute X = 30.  1. <= Y <= 2.
        Bord Haut3  Y = 2.  17. <= X <= 30.
    \} ,
    Pave Bas
    \{
        Origine 7. 0.
        Nombre_de_Noeuds 11 6 
        Longueurs 10. 1.
    \}
    \{
        Bord Bas2   Y = 0.  7. <= X <= 17.
        Bord Gauche X = 7.  0. <= Y <= 1.
    \} ,
    Pave SBasse
    \{
        Origine 17. 0.
        Nombre_de_Noeuds 14 6 
        Longueurs 13. 1.
    \}
    \{
        Bord SortieBasse X = 30. 0. <= Y <= 1.
        Bord Bas3   Y = 0. 17. <= X <= 30.
    \}
\}
{\bf{Sous_Zone zone}}
{\bf{Associate zone dom}}
{\bf{Lire zone }}
{\bf{\{ }}
    {\bf{Rectangle}}
    {\bf{Origine 15 0.5}}
    {\bf{Cotes   1 1}}
{\bf{\} }}
# END MESH #
# BEGIN PARTITION
Partition dom
\{
    Partitionneur tranche \{ tranches 2 1 \}
    Larg_joint 1
    Nom_Zones DOM
\}
Fin
END PARTITION #
# BEGIN SCATTER
Scatter DOM.Zones dom
END SCATTER #
VDF dis
schema_Euler_explicite sch
Lire sch
\{
    tinit 0
    tmax 32.
    dt_min 0.01
    dt_max 0.01
    dt_impr 0.1
    dt_sauv 1000.
    seuil_statio 1.e-8
\}
Fluide_Incompressible fluide
Lire fluide
\{
    mu Champ_Uniforme 1 3.7e-05
    rho Champ_Uniforme 1 2
    {\bf{beta_co Champ_Uniforme 1 0. }}
\}
{\bf{Constituant c1}}
{\bf{Lire c1}}
{\bf{\{ }}
{\bf{    coefficient_diffusion Champ_Uniforme 3 1. 1. 1. }}
{\bf{\} }}
{\bf{Champ_Uniforme gravite}}
{\bf{Lire gravite 2 0 0 }}
{\bf{Associate fluide gravite }}
Associate pb dom
Associate pb sch
Associate pb fluide
Associate pb c1
Discretize pb dis
Lire pb
\{
    Navier_Stokes_turbulent
    \{
        solveur_pression cholesky \{ \}
        convection \{ Amont \}
        diffusion \{ \}
        conditions_initiales \{ vitesse Champ_Uniforme 2 0. 0. \}
        boundary_conditions
        \{
             Haut1 Paroi_Fixe
             Bas1 Paroi_Fixe
             Haut2 Paroi_Fixe
             Bas2 Paroi_Fixe
             Haut3 Paroi_Fixe
             Bas3 Paroi_Fixe
             Gauche Paroi_Fixe
             SortieBasse frontiere_ouverte_pression_imposee Champ_Front_Uniforme 1 0.
             SortieHaute frontiere_ouverte_pression_imposee Champ_Front_Uniforme 1 0.
             Entree frontiere_ouverte_vitesse_imposee Champ_Front_Uniforme 2  1. 0.
        \}
        modele_turbulence K_Epsilon
        \{
            Transport_K_Epsilon 
            \{
                convection \{ amont \}
                diffusion \{ \}
                sources \{ Source_Transport_K_Eps_aniso_concen \{ C1_eps 1.44 C2_eps 1.92 C3_eps 1. \} \}
                boundary_conditions
                \{
                    Haut1 Paroi
                    Bas1 Paroi
                    Haut2 Paroi
                    Bas2 Paroi
                    Haut3 Paroi
                    Bas3 Paroi
                    Gauche Paroi
                    Entree frontiere_ouverte_K_eps_impose Champ_Front_Uniforme 2 1.e-2 1.e-3
                    SortieBasse frontiere_ouverte K_EPS_EXT Champ_Front_Uniforme 2 0. 0.
                    SortieHaute frontiere_ouverte K_EPS_EXT Champ_Front_Uniforme 2 0. 0.
                \}
                conditions_initiales \{ k_Eps Champ_Uniforme 2 0. 0. \}
             \}
             Prandtl_K 1
             Prandtl_Eps 1.3
             turbulence_paroi loi_expert_hydr \{ kappa 0.415 Erugu 9.11 A_plus 26 \} dt_impr_ustar 10. eps_min 1.e-15
        \}
    \}
    {\bf{Convection_diffusion_Concentration_turbulent }}
    {\bf{\{ }}
        {\bf{diffusion \{ \} }}
        {\bf{convection \{ quick \} }}
        {\bf{sources \{ Source_constituant Champ_uniforme_morceaux dom 3 \{ Defaut 0 0 0 zone 0 1 0 \} \} }}
        {\bf{boundary_conditions }}
        {\bf{\{ }}
             {\bf{Haut1          Paroi }}
             {\bf{Bas1           Paroi }}
             {\bf{Haut2          Paroi }}
             {\bf{Bas2           Paroi }}
             {\bf{Haut3          Paroi }}
             {\bf{Bas3           Paroi }}
             {\bf{Gauche         Paroi }}
             {\bf{SortieBasse    frontiere_ouverte C_ext Champ_Front_Uniforme 3 0. 0. 0. }}
             {\bf{SortieHaute    frontiere_ouverte C_ext Champ_Front_Uniforme 3 0. 0. 0. }}
             {\bf{Entree         frontiere_ouverte C_ext Champ_Front_Uniforme 3 0. 0. 0. }}
        {\bf{\} }}
        {\bf{conditions_initiales \{ concentration Champ_Uniforme 3 0. 0. 0. \} }}
        {\bf{Modele_turbulence Schmidt \{ }}
            {\bf{Turbulence_paroi loi_standard_hydr_scalaire }}
        {\bf{\} }}
    {\bf{\} }}
    Postraitement 
    \{
        Sondes 
        \{
            sonde_vitesse vitesse periode 0.01 points 1 10. 0.5
            sonde_k k periode 0.01 points 1 9.5 0.5
            sonde_eps eps periode 0.01 points 1 9.5 0.5
            sonde_visc viscosite_turbulente periode 0.01 points 1 9.5 0.5
            sonde_yplus y_plus periode 0.01 segment 9 7.5 0.01 16.5 0.01
            sonde_vorticite vorticite periode 0.01 segment 9 7.5 0.01 16.5 0.01
        \}
        {\bf{format lata}}
        Champs dt_post 20.
        \{
            pression elem
            pression som
            vitesse elem
            vitesse som
            k elem
            k som
            eps elem
            eps som
            viscosite_turbulente elem
            viscosite_turbulente som
            {\bf{concentration0 elem}}
            {\bf{concentration1 elem}}
            {\bf{concentration2 elem}}
        \}
    \}
\}
Solve pb
Fin
\end{alltt}
